Verifying Spatial Properties of Array Computations

### 2017-04-18 oopsla17/model.tex
fix model.tex

We mark in our model the presence of modifiers such as
\texttt{readOnce} and \texttt{atMost}.  Approximation modifiers are interpreted as
injections into the $\mathsf{Approx}$ variant by $\interpApprox{}$ in
\Cref{subfig:modifier-model}.  The $\textsf{Approx}$ type corresponds
to the presence or absence of the spatial approximation modifier, with
\textsf{exact} when there is no such modifier and \textsf{lower} and
\textsf{upper} for \term{atLeast} and \term{atMost}. In a similar way,
multiplicity modifiers are interpreted as injections in the
$\mathsf{Mult}$ variant by $\interpMult{}$, corresponding to the to
the presence or absence of the \term{readOnce} modifier as shown in
\Cref{subfig:modifier-model}.

>>>>

We mark in our model the presence of modifiers such as
\texttt{readOnce} and \texttt{atMost}.  Approximation modifiers are interpreted as
injections into the $\mathsf{Approx}$ variant by $\interpApprox{-}$ in
\Cref{subfig:modifier-model}.  The $\textsf{Approx}$ type corresponds
to the presence or absence of the spatial approximation modifier, with
\textsf{exact} when there is no such modifier and \textsf{lower} and
\textsf{upper} for \term{atLeast} and \term{atMost}. In a similar way,
multiplicity modifiers are interpreted as injections in the
$\mathsf{Mult}$ variant by $\interpMult{-}$, corresponding to
the presence or absence of the \term{readOnce} modifier as shown in
\Cref{subfig:modifier-model}.
